Unifying the communicable disease spreading paradigm with Gompertzian growth

### 2023-04-05 arxiv/main.tex
subtitle change

\subsection*{A closed-form expression for a unified model}
Finally, we are positioned to arrive at a closed-form expression for a finite number of interaction terms in this modified logistic model, which represents the infection term in the SIR model. Working with a single unitless growth variable and omitting the multivariate network without loss of generality, we start with

>>>>

\subsection*{A closed-form expression for a unified Gompertz-Logistic model}
Finally, we are positioned to arrive at a closed-form expression for a finite number of interaction terms in this modified logistic model, which represents the infection term in the SIR model. Working with a single unitless growth variable and omitting the multivariate network without loss of generality, we start with
